%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Analyzing Sejong City Real-Estate Market Data for Korea Land and Housing Corporation} % Job title
    {Sejong City Real-Estate Market Analyzing Competition: The First Prize} % Organization
    {LH COMPAS, Seongnam} % Location
    {Feb. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed and visualized the real-estate trading, population, news article data of Sejong City with Python.}
        \item {Implemented models such as LDA, HDBSCAN Clustering, Linear Regression on the data to find insights. }
        \item {Organized the characteristics of Sejong and made a presentation about our analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Option Value Calculating and Visualizing Package for Python} % Job title
    {Financial Engineering Research Competition: The First Prize} % Organization
    {Korea University, Seoul} % Location
    {Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote codes to implement option valuation models in Python.}
        \item {Made user guides and example codes for the package and uploaded on the GitHub.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Analyzing trading data to profile investment behavior of 2,30's} % Job title
    {NH Investor Profiling Competition: Finalist} % Organization
    {NH Investment Bank, Seoul} % Location
    {Nov. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed and visualized the stock trading data with Python.}
        \item {Found insights from the data and made marketing suggestions for NH Investment Bank.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Economic Research: Reasons of Youth Unemployment} % Job title
    {Jinri Scholarship} % Organization
    {Korea University, Seoul} % Location
    {May. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the youth unemployment model for our hypothesis test.}
        \item {Gathered and analyzed the wage data with Python and R.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
